An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-09-15 CMPSpaper_writing/CMPSpaper_writing.Rmd
comments added

default parameters can be beaten?
cmps.diff, cmps.maxbar and their scaled version are good? we suggest cmps.diff_scaled since it's more comparable and summarizes more information?
Note that the goal of these comparisons is not to determine the optimal set of parameters for the CMPS algorithm, but to show a general procedure that can be used for

>>>>

cmps.max is not the best metric to measure similarity 
the one we prefer
cmps.diff, cmps.maxbar and their scaled version are good? we suggest cmps.diff_scaled since it's more comparable and summarizes more information?

parameters need cross-validation
choice of parameters depends on resolution ( scanning process ) and the data set
determining the source is a harder task for Hamby 44 than for Hamby 252 
default parameters can be beaten?

Note that the goal of these comparisons is not to determine the optimal set of parameters for the CMPS algorithm, but to show a general procedure that can be used for 
a larger database that is representative
procedure that could be used to reach that point

**Comparing with Random Forest**

Introduce the work , cite the paper 
CSAFE trained
